### 2022-03-15 manuscript.tex
ong [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/9213662b7adaf086956a4d1fa83ad98751f19610.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/9213662b7adaf086956a4d1fa83ad98751f19610/checks
https://github.com/scherzerthesis/thesis/actions/runs/1988423983

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/1641e91da2ea2e649fd5023d29243d56df558151/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/1641e91da2ea2e649fd5023d29243d56df558151}{scherzerthesis/thesis@1641e91}
on March 15, 2022.

@@

\begin{figure}
\hypertarget{fig:11}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/figure.svg}
\caption{\textbf{Differential BRAF\textsuperscript{V600E} lung tumorigenesis imparted by p53-Hotspot mutants.} \textbf{(A)} Genetically-engineered alleles of \emph{Braf\textsuperscript{v600E}} and \textsuperscript{Trp53} before and after Cre-Recombinase. \textbf{(B)} Tumor burden and \emph{(C)}** Tumor size of BRAF(V600E) plus Trp53-wildtype, null, or mutant alleles 14 weeks post Cre-mediated recombination. \emph{(D)} Representative H\&E images 14 weeks after Cre-recombination. \textbf{(E)} Survival of mice with Heterozygous \emph{Trp53} mutant alleles. \textbf{(F)} Survival of mice with homozygous \emph{Trp53} alleles.}\label{fig:11}
}
\end{figure}

\begin{figure}
\hypertarget{fig:12}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/figure2_021722.svg}
\caption{\textbf{Missense mutant-p53 alters lung adenocarcinoma differentiation status and accumulation of mutant-p53 correlates with p19 ARF expression.} \textbf{(A)} Panel representative IHC sections stained with SPC,NKX2-1, p53 and HMGA2. \textbf{(B)} H-score of individual tumors. \textbf{(C)} Association between mutant-p53 R172H accumulation and increased malignancy and dedifferentiation. \textbf{(D)} serial section of P53-HI and pERK1/2-HI tumors compared to adjacent low. \textbf{(E)} Colocalization of p19/ARF and p53 in p53-mutant tumors}\label{fig:12}
}
\end{figure}

\begin{figure}
\hypertarget{fig:13}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/figure3_021722.svg}
\caption{\textbf{Mutant-p53 cell lines are refractory to BRAFi+MEKi.} \textbf{(A)} Response of GEMMs to BRAFi+MEKi chow after four weeks \textbf{(B)} in vitro dose response to BRAFi single agent. \textbf{(C)} in vitro timecourse with dabrafenib (1000nm) plus trametinib (100nM). \textbf{(D)} Accumulation of dead cells in dabrafenib plus trametinib measured by CytotoxRed accumulation. \textbf{(E)} Immunoblotting of phospho-ERK1/2 in response to dabrafenib plus trametinib. \textbf{(F)} Ectopic expression of p53\textsuperscript{R17H} in human HCC364 cells. \textbf{(E)} Response of p53\textsuperscript{R175H} cells to dabrafenib plus trametinib.}\label{fig:13}
}
\end{figure}

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/figure4_021722.svg}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/9213662b7adaf086956a4d1fa83ad98751f19610/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/9213662b7adaf086956a4d1fa83ad98751f19610}{scherzerthesis/thesis@9213662}
on March 15, 2022.

@@

\begin{figure}
\hypertarget{fig:11}{%
\centering
\includegraphics[width=0.1\textwidth,height=\textheight]{images/p53_1.png}
\caption{\textbf{Differential BRAF\textsuperscript{V600E} lung tumorigenesis imparted by p53-Hotspot mutants.} \textbf{(A)} Genetically-engineered alleles of \emph{Braf\textsuperscript{v600E}} and \textsuperscript{Trp53} before and after Cre-Recombinase. \textbf{(B)} Tumor burden and \emph{(C)}** Tumor size of BRAF(V600E) plus Trp53-wildtype, null, or mutant alleles 14 weeks post Cre-mediated recombination. \emph{(D)} Representative H\&E images 14 weeks after Cre-recombination. \textbf{(E)} Survival of mice with Heterozygous \emph{Trp53} mutant alleles. \textbf{(F)} Survival of mice with homozygous \emph{Trp53} alleles.}\label{fig:11}
}
\end{figure}

\begin{figure}
\hypertarget{fig:12}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_2.png}
\caption{\textbf{Missense mutant-p53 alters lung adenocarcinoma differentiation status and accumulation of mutant-p53 correlates with p19 ARF expression.} \textbf{(A)} Panel representative IHC sections stained with SPC,NKX2-1, p53 and HMGA2. \textbf{(B)} H-score of individual tumors. \textbf{(C)} Association between mutant-p53 R172H accumulation and increased malignancy and dedifferentiation. \textbf{(D)} serial section of P53-HI and pERK1/2-HI tumors compared to adjacent low. \textbf{(E)} Colocalization of p19/ARF and p53 in p53-mutant tumors}\label{fig:12}
}
\end{figure}

\begin{figure}
\hypertarget{fig:13}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_3.png}
\caption{\textbf{Mutant-p53 cell lines are refractory to BRAFi+MEKi.} \textbf{(A)} Response of GEMMs to BRAFi+MEKi chow after four weeks \textbf{(B)} in vitro dose response to BRAFi single agent. \textbf{(C)} in vitro timecourse with dabrafenib (1000nm) plus trametinib (100nM). \textbf{(D)} Accumulation of dead cells in dabrafenib plus trametinib measured by CytotoxRed accumulation. \textbf{(E)} Immunoblotting of phospho-ERK1/2 in response to dabrafenib plus trametinib. \textbf{(F)} Ectopic expression of p53\textsuperscript{R17H} in human HCC364 cells. \textbf{(E)} Response of p53\textsuperscript{R175H} cells to dabrafenib plus trametinib.}\label{fig:13}
}
\end{figure}

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics{images/p53_5.png}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics{images/p53_6.png}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics{images/p53_7.png}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics{images/p53_8.png}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}
